---
title: "Developing Data Products Course Project"
author: "ZTH"
date: "2020/10/4"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Diamond Analysis Report
- This is a report created by Rmarkdown slidy presentation
- In this R slidy presentation, the dataset I choose and the usage of my shiny App are showed as follows
- Use PageUp and PageDown to traverse all the slides


## The Dataset I Choose in My Shiny Application
In this application, I choose diamonds dataset for analysis.Here is a brief overview of it.
```{r,warning=FALSE}
library(ggplot2)
data("diamonds")
head(diamonds,5)
```


## What My Shiny Application is about
- The price of diamonds have correlations with many attributes in the dataset.
- The relationship between variable "price" and "caret" is plotted in this App, with scatter plot and regression line.
- The attributes "cut" and "clarity" are factor variables. They are used for choosing the specific points showed in the plot above.
- You can use choice box to choose the specific cut and clarity.

## Online Shiny App and Github repo
- Here is my Shiny App published on server  
<https://zth123456.shinyapps.io/developing_data_products/>  
- Here is my Github repo of this whole course project  
<https://github.com/997-icu/Course-Project-Shiny-Application-and-Reproducible-Pitch>


